method

### 2022-02-18 06_Paper/ER-ED/method.Rmd
added comment

Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence (Bradley & Lang, 2000).
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).
The ground electrode will be placed over the left *Mastoid*.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 kΩ. 
Data will be sampled at 1000 Hz, filtered, rectified and integrated. 
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presenation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf. Bradley & Lang, 2000). 
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
<!-- AG: insert references -->

>>>>

Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence (Bradley & Lang, 2000). <!-- Quelle noch einfügen -->
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986). <!-- Quelle einfügen -->
The ground electrode will be placed over the left *Mastoid*.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 kΩ. 
Data will be sampled at 1000 Hz, filtered, rectified and integrated. 
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presenation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf. Bradley & Lang, 2000). 
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
<!-- AG: insert references -->
